Figures

### 2020-12-21 inst/manuscript/figures.Rmd
Revised segmentation stats--decided to just stick with original approach (compare against validation grids, not multiple scales)

### Figure S9: Segmentation statistics
```{r segstats, eval=FALSE}
data("top_label_data")
data("field_validation_stats")

human <- top_label_data$stats %>%
  mutate(mu_prop = NA, type = "Validation") %>%
  select(-contains("id"))
machine <- field_validation_stats %>%
  mutate(type = "Segmentation")
humachine <- bind_rows(human, machine) %>% 
  mutate(aoi = as.numeric(gsub("labeller", "", aoi))) %>% 
  arrange(aoi)

# Summarize AOI-wise averages (field size)
humachine_sum <- humachine %>% group_by(aoi, type) %>% 
  summarize(Median = median(Mean), Mean = mean(Mean)) %>% 
  ungroup() %>% 
  tidyr::pivot_longer(cols = Median:Mean, names_to = "Stat")
# field number
humachine_sum_n <- humachine %>% group_by(aoi, type) %>% 
  summarize(Median = median(n), Mean = mean(n)) %>% 
  ungroup() %>% 
  tidyr::pivot_longer(cols = Median:Mean, names_to = "Stat")

@@

# Field size
p <- ggplot(humachine) + 
  geom_density(aes(x = Mean, y = ..count.., fill = type), col = "transparent", 
               linetype = "blank") +  
  geom_vline(data = humachine_sum, 
             aes(xintercept = value, color = type, linetype = Stat), 
             size = 0.5) +
  scale_x_continuous(expand = c(0.03, 0.03), breaks = brks, limits = c(0, 30)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_color_manual(name = "", values = c("blue", "red"), guide = FALSE) + 
  scale_fill_manual(name = "", values = fcols) +  
  # scale_linetype_manual(name = "", values = c("dashed", "solid")) +  
  scale_linetype("") +  
  facet_wrap(vars(aoi)) + 
  xlab("Field size (ha)") + ylab("Count") + 
  theme_fun()
ggsave(pth("figures/si_validation_stats_fha.png"), 
       width = 7, height = 7, units = "in", dpi = 300)

# field number
brks <- seq(0, 20, 5)
p2 <- ggplot(humachine) + 
  geom_density(aes(x = n, y = ..count.., fill = type), col = "transparent", 
               linetype = "blank") +  
  geom_vline(data = humachine_sum_n, 
             aes(xintercept = value, color = type, linetype = Stat), 
             size = 0.5) +
  scale_x_continuous(expand = c(0.03, 0.03), breaks = brks, limits = c(0, 20)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 40)) +
  scale_color_manual(name = "", values = c("blue", "red"), guide = FALSE) + 
  scale_fill_manual(name = "", values = fcols) +  
  # scale_linetype_manual(name = "", values = c("dashed", "solid")) +  
  scale_linetype("") +  
  facet_wrap(vars(aoi)) + 
  xlab("Number of fields") + ylab("Count") + 
  theme_fun()
ggsave(pth("figures/si_validation_stats_fn.png"), 
       width = 7, height = 7, units = "in", dpi = 300)

@@

>>>>

### Figure S9: Segmentation statistics (grid scale)

[Check whether the means need to be weighted or not]
[Check whether need to redo median]
```{r segstats, eval=FALSE}
# data("top_label_data")
# data("field_validation_stats")
data("segment_quality_stats")
# data
datnms <- c("top_label_data", "field_validation_stats",
            "tile_aoi_validation_stats")
for(i in datnms) {
  load(system.file(glue::glue("extdata/{i}.rda"), package = "activemapper"))
}

# extract distributions
human <- top_label_data$stats %>%
  mutate(mu_prop = NA, type = "Validation") %>%
  select(-contains("id"))
machine <- field_validation_stats %>%
  mutate(type = "Segmentation")
humachine <- bind_rows(human, machine) %>%
  mutate(aoi = as.numeric(gsub("labeller", "", aoi))) %>%
  arrange(aoi)

squal <- segment_quality_stats %>% 
  filter(scale == "grid" & aoi != "All") %>% 
  mutate(aoi = as.numeric(aoi))
# 
# # Summarize AOI-wise averages (field size)
# humachine_sum <- humachine %>% group_by(aoi, type) %>% 
#   summarize(Median = median(Mean), Mean = mean(Mean)) %>% 
#   ungroup() %>% 
#   tidyr::pivot_longer(cols = Median:Mean, names_to = "Stat")
# # field number
# humachine_sum_n <- humachine %>% group_by(aoi, type) %>% 
#   summarize(Median = median(n), Mean = mean(n)) %>% 
#   ungroup() %>% 
#   tidyr::pivot_longer(cols = Median:Mean, names_to = "Stat")

@@

# Field size
p <- ggplot(humachine) + 
  geom_density(aes(x = Mean, y = ..count.., fill = type), col = "transparent", 
               linetype = "blank") +  
  geom_vline(data = squal %>% filter(measure == "area"), 
             aes(xintercept = value, color = type, linetype = Stat), 
             size = 0.5) +
  scale_x_continuous(expand = c(0.03, 0.03), breaks = brks, limits = c(0, 30)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_color_manual(name = "", values = c("blue", "red"), guide = FALSE) + 
  scale_fill_manual(name = "", values = fcols) +  
  # scale_linetype_manual(name = "", values = c("dashed", "solid")) +  
  scale_linetype("") +  
  facet_wrap(vars(aoi)) + 
  xlab("Field size (ha)") + ylab("Count") + 
  theme_fun()
ggsave(pth("figures/si_validation_stats_fha2.png"), 
       width = 7, height = 7, units = "in", dpi = 300)

# field number
brks <- seq(0, 20, 5)
p2 <- ggplot(humachine) + 
  geom_density(aes(x = n, y = ..count.., fill = type), col = "transparent", 
               linetype = "blank") +  
  geom_vline(data = squal %>% filter(measure == "n"), 
             aes(xintercept = value, color = type, linetype = Stat), 
             size = 0.5) +
  scale_x_continuous(expand = c(0.03, 0.03), breaks = brks, limits = c(0, 20)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 40)) +
  scale_color_manual(name = "", values = c("blue", "red"), guide = FALSE) + 
  scale_fill_manual(name = "", values = fcols) +  
  # scale_linetype_manual(name = "", values = c("dashed", "solid")) +  
  scale_linetype("") +  
  facet_wrap(vars(aoi)) + 
  xlab("Number of fields") + ylab("Count") + 
  theme_fun()
ggsave(pth("figures/si_validation_stats_fn2.png"), 
       width = 7, height = 7, units = "in", dpi = 300)

@@

<!-- ### Figure S10: Segmentation statistics, tile scale -->
<!-- ```{r, eval=FALSE} -->
<!-- data("tile_aoi_validation_stats") -->

<!-- humachine <- tile_aoi_validation_stats$tile %>%  -->
<!--   mutate(type = ifelse(grepl("segments", type), "Segmentation", type), -->
<!--          type = ifelse(grepl("validation", type), "Validation", type)) %>%  -->
<!--   select(type, aoi, tile, area_mu, area_med, n_mu) %>%  -->
<!--   rename(Mean = area_mu, Median = area_med) -->

<!-- humachine_sum <- humachine %>% group_by(aoi, type) %>%  -->
<!--   summarize(Median = median(Mean), Mean = mean(Mean)) %>%  -->
<!--   ungroup() %>%  -->
<!--   tidyr::pivot_longer(cols = Median:Mean, names_to = "Stat") -->

<!-- humachine_sum_n <- humachine %>% group_by(aoi, type) %>%  -->
<!--   summarize(Median = median(n_mu), Mean = mean(n_mu)) %>%  -->
<!--   ungroup() %>%  -->
<!--   tidyr::pivot_longer(cols = Median:Mean, names_to = "Stat") -->

<!-- # Field size -->
<!-- brks <- seq(0, 20, 5) -->
<!-- p <- ggplot(humachine) +  -->
<!--   geom_density(aes(x = Mean, y = ..count.., fill = type), col = "transparent",  -->
<!--                linetype = "blank") +   -->
<!--   geom_vline(data = humachine_sum,  -->
<!--              aes(xintercept = value, color = type, linetype = Stat),  -->
<!--              size = 0.5) + -->
<!--   scale_x_continuous(expand = c(0.03, 0.03), breaks = brks, limits = c(0, 20)) + -->
<!--   scale_y_continuous(expand = c(0, 0)) + -->
<!--   scale_color_manual(name = "", values = c("blue", "red"), guide = FALSE) +  -->
<!--   scale_fill_manual(name = "", values = fcols) +   -->
<!--   # scale_linetype_manual(name = "", values = c("dashed", "solid")) +   -->
<!--   scale_linetype("") +   -->
<!--   facet_wrap(vars(aoi)) +  -->
<!--   xlab("Field size (ha)") + ylab("Count") +  -->
<!--   theme_fun() -->
<!-- ggsave(pth("figures/si_tile_validation_stats_fha.png"),  -->
<!--        width = 7, height = 7, units = "in", dpi = 300) -->

<!-- # field number -->
<!-- brks <- seq(0, 20, 5) -->
<!-- p2 <- ggplot(humachine) +  -->
<!--   geom_density(aes(x = n_mu, y = ..count.., fill = type), col = "transparent",  -->
<!--                linetype = "blank") +   -->
<!--   geom_vline(data = humachine_sum_n,  -->
<!--              aes(xintercept = value, color = type, linetype = Stat),  -->
<!--              size = 0.5) + -->
<!--   scale_x_continuous(expand = c(0.03, 0.03), breaks = brks, limits = c(0, 20)) + -->
<!--   scale_y_continuous(expand = c(0, 0)) + #, limits = c(0, 40)) + -->
<!--   scale_color_manual(name = "", values = c("blue", "red"), guide = FALSE) +  -->
<!--   scale_fill_manual(name = "", values = fcols) +   -->
<!--   # scale_linetype_manual(name = "", values = c("dashed", "solid")) +   -->
<!--   scale_linetype("") +   -->
<!--   facet_wrap(vars(aoi)) +  -->
<!--   xlab("Number of fields") + ylab("Count") +  -->
<!--   theme_fun() -->
<!-- ggsave(pth("figures/si_tile_validation_stats_fn.png"),  -->
<!--        width = 7, height = 7, units = "in", dpi = 300) -->
<!-- ``` -->

<!-- ### Figure S11: Segmentation statistics: grid, tile, and AOI scales -->

<!-- Read back in segments to get distributions -->
<!-- ```{r, eval = FALSE} -->
<!-- data("tile_aoi_validation_stats") -->

<!-- # # Read in segments, drop old AOI3 -->
<!-- # segment_files <- dir(here("external/data/results/segments/merged"), -->
<!-- #                      pattern = "boundarymerge", full.names = TRUE) -->
<!-- # iid <- as.numeric(gsub("[[:alpha:]]|_|\\.", "", basename(segment_files))) -->
<!-- # segment_files <- tibble(file = segment_files, order = iid) %>% arrange(iid) -->
<!-- # segment_files <- segment_files %>% filter(!grepl("aoi3_*.*merge.geojson", file)) -->
<!-- #  -->
<!-- # # area and quiet func -->
<!-- # ha <- function(x) as.numeric(units::set_units(st_area(x), "ha")) -->
<!-- # quiet <- function(x) suppressWarnings(suppressMessages(x)) -->

<!-- humachine_sum <- tile_aoi_validation_stats$aoi %>%  -->
<!--   select(type, aoi, area_mu, area_med) %>%  -->
<!--   rename(Mean = area_mu, Median = area_med) %>%  -->
<!--   tidyr::pivot_longer(cols = Median:Mean, names_to = "Stat") %>%  -->
<!--   tidyr::pivot_wider(names_from = type, values_from = value) -->

<!-- aoi_wide <- tile_aoi_validation_stats$aoi %>% group_by(type) %>%  -->
<!--   summarize(Mean = weighted.mean(area_mu, w = n),  -->
<!--             Median = weighted.mean(area_med, w = n)) %>%  -->
<!--   tidyr::pivot_longer(cols = Median:Mean, names_to = "Stat") %>%  -->
<!--   tidyr::pivot_wider(names_from = type, values_from = value) %>%  -->
<!--   mutate(aoi = "All") %>% select(aoi, !!names(.)) -->

<!-- p <- ggplot(humachine_sum) + -->
<!--   geom_point(aes(x = segments, y = validation)) +  -->
<!--   geom_point(data = aoi_wide, aes(x = segments, y = validation), color = "red") +  -->
<!--   scale_x_continuous(limits = c(0, 8)) +  -->
<!--   scale_y_continuous(limits = c(0, 8)) +  -->
<!--   ggrepel::geom_text_repel( -->
<!--     aes(label = aoi, x = segments, y = validation), col = "grey50",  -->
<!--     segment.color = "grey60", point.padding = 0.1, min.segment.length = 0.2, -->
<!--     segment.size = 0.2, size = 3    -->
<!--   ) +  -->
<!--   xlab("Segmentation field size (ha)") + ylab("Validation field size (ha)") +  -->
<!--   geom_abline(slope = 1) + facet_wrap(vars(Stat)) +  -->
<!--   theme_linedraw() +  -->
<!--   theme(strip.background = element_rect(fill = "white"),  -->
<!--         strip.text = element_text(colour = "black")) -->

<!-- ``` -->
